A data-intensive assessment of the species-abundance distribution.

### 2015-04-02 defense_pres.tex
Adds more logos.

%\begin{frame}
%\tableofcontents
%\end{frame}
\section{Usage Notes}
\begin{frame}
\frametitle{Open science}
\begin{itemize}
\item Code: 
\begin{itemize}
\item github.com/embaldridge
\item github.com/weecology
\end{itemize}
\item Data: figshare.com
\item Twitter: @elitabaldridge
\end{itemize}
\includegraphics[scale=.5]{./sad-data/dissertation/Open_Access.png}  
\includegraphics[scale=.4]{./sad-data/dissertation/osi_logo.png}
\end{frame}

>>>>

%\begin{frame}
%\tableofcontents
%\end{frame}
\section{Usage Notes}
\begin{frame}
\frametitle{Open science}
\begin{itemize}
\item Code: 
\begin{itemize}
\item github.com/embaldridge
\item github.com/weecology
\end{itemize}
\item Data: figshare.com
\item Twitter: @elitabaldridge
\end{itemize}
\begin{center}
\includegraphics[scale=.40]{./sad-data/dissertation/GitHub-Mark-120px-plus.png}
\includegraphics[scale=.45]{./sad-data/dissertation/figshare_FullColour.jpg} 
\includegraphics[scale=.2]{./sad-data/dissertation/Open_Access.png}  
\includegraphics[scale=.15]{./sad-data/dissertation/osi_logo.png}

\end{center}
\end{frame}
